AggregateCounts

### 2021-06-22 R/AggregateCounts.Rmd
trying to setup biomass per slice here

```{r fancy histogram of aggregates}

@@

```{r biomass per slice}
#this was taken from "Microscopy data clean.Rmd"
GetResults<-function(){
  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/wtd1-02')
  fileList<-list.files(path = folder, full.names = TRUE)
  blueChannel<-fileList[grep('B_',fileList)]
  redChannel<-fileList[grep('R_',fileList)]
  greenChannel<-fileList[grep('G_',fileList)]
  Results<-rbind(blueChannel,redChannel,greenChannel)
  Results<-Results %>% mutate(Sample = sample)
IterateTiff<-function(fileList, species)
  growth<-matrix(ncol=3, nrow=length(fileList))
  for(slice in 1:(length(fileList))){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }
  growthDf<-data.fram(growth)
return(growthDf) 
  }

>>>>

```{r fancy histogram of aggregates !!!deprecated}

@@

```{r biomass per slice}
#this was taken from "Microscopy data clean.Rmd"
GetResults<-function(){
  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images'
  samplesList<-list.files(path = folder, full.names = TRUE)
  imagesList<-mapply(list.files,samplesList)

separateColors
  blueChannel<-fileList[grep('B_',fileList)]
  redChannel<-fileList[grep('R_',fileList)]
  greenChannel<-fileList[grep('G_',fileList)]
  Results<-rbind(blueChannel,redChannel,greenChannel)
  Results<-Results %>% mutate(Sample = sample)

   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}

  VectorizeTiff<-function(file){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }

  IterateTiff<-function(fileList, species)
  growth<-matrix(ncol=3, nrow=length(fileList))
  for(slice in 1:(length(fileList))){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }
  growthDf<-data.fram(growth)
return(growthDf) 
  }
